### 2016-01-14 trunk/targetDP/doc/execution_model.tex
updating spec
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig@2815 40876441-3496-0410-a613-a2fca35b2ae2

To ensure that the target function has completed, a
\verb+targetSynchronize+ statement should follow the code location
where target function is launched. When the initial thread encounters
this statement, it will wait until the target region has completed. It
is possible for the initial thread to execute other instructions
(which do not depend on the results of the target function), after the
function launch but before the synchronisation call. This may result in
overlapping of host and target execution, and hence optimisation, in
some implementations. Once the target function has completed, the
initial thread will continue sequentially until another target
function launch is encountered.

@@

\begin{comment}
Possibly add targetSyncThreads() to
  allow communication within target functions?]
\end{comment}

\begin{comment}
Some text on reductions needed.
\end{comment}

>>>>

To ensure that the target function has completed, a
\verb+targetSynchronize+ statement should follow the code location
where target function is launched. When the initial thread encounters
this statement, it will wait until the target region has completed. It
is possible, in principle, for the initial thread to execute other instructions
(which do not depend on the results of the target function), after the
function launch but before the synchronisation call. This may result in
overlapping of host and target execution, and hence optimisation, in
some implementations. Once the target function has completed, the
initial thread will continue sequentially until another target
function launch is encountered.

@@

In applications, it is sometimes necessary to perform reductions,
where multiple data values are combined in a certain way. For example,
values existing on each grid point may be summed into a single total
value. The targetDP model supports such operations in a simplistic
way. It is the responsibility of the application to create the array
of values (using standard targetDP functionality) to act as the input
to the reduction operation. The application can then pass this array
to the API function corresponding to the desired reduction operation
(e.g. \verb+targetDoubleSum+ for the summation of an array of
double-precision Values). If the required reduction operation does not yet
exist, the user can simply extend the targetDP API using existing
functionality as a template.
